### 2016-06-16 README.Rmd
woops, thought ion was down for good, guess it was just a hiccup ion back in readme back with ion info
readme https udpate for a link

The `taxize` tutorial is can be found at [http://ropensci.org/tutorials/taxize.html][tut].

@@

>>>>

The `taxize` tutorial is can be found at [https://ropensci.org/tutorials/taxize.html][tut].

@@

	<td style="text-align:left;">Index of Names (ION)</td>
	<td style="text-align:left;"><code>ion</code></td>
	<td style="text-align:left;"><a href="http://www.organismnames.com/">link</a></td>
